\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[left=2cm,right=2cm,top=2cm,bottom=2cm]{geometry}
\usepackage{hyperref}
\usepackage{longtable}
\usepackage{booktabs}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{enumitem}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
    pdftitle={ETG Certification Fixes - Coast to Coast Journeys},
}

\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}

\lstdefinestyle{mystyle}{
    backgroundcolor=\color{backcolour},   
    commentstyle=\color{codegreen},
    keywordstyle=\color{magenta},
    numberstyle=\tiny\color{codegray},
    stringstyle=\color{codepurple},
    basicstyle=\ttfamily\footnotesize,
    breakatwhitespace=false,         
    breaklines=true,                 
    captionpos=b,                    
    keepspaces=true,                 
    numbers=left,                    
    numbersep=5pt,                  
    showspaces=false,                
    showstringspaces=false,
    showtabs=false,                  
    tabsize=2
}

\lstset{style=mystyle}

\title{ETG Certification Final Audit Report \\ \large Coast to Coast Journeys - Fixed Resolutions for 3rd Update}
\author{Engineering Team - Coast to Coast Journeys}
\date{March 5, 2026}

\begin{document}

\maketitle

\section{Introduction}
This document serves as the final response to the Third Update of the ETG / RateHawk Certification. All pending items have been re-verified through technical simulation and code audit. We have addressed critical concerns regarding RPM limits, policy display, room matching logic, and guest configuration.

\section{System Configuration}

\begin{itemize}[leftmargin=1.5cm]
    \item \textbf{API Key ID}: 83 (Applied to all search and booking requests).
    \item \textbf{Static IP for Whitelist}: \texttt{136.116.198.82}
    \item \textbf{SLA Compliance}: 180-second booking timeout implemented.
\end{itemize}

\section{Standard Workflow Integration}

\begin{longtable}{lllp{5cm}}
\toprule
\textbf{Step Name} & \textbf{User Action / Logic} & \textbf{ETG Endpoint} \\
\midrule
User Search & Select destination, dates, and guests & /search/serp/hotels/ \\
Hotel List & Show hotel cards with ratings/prices & Local Database (Static) \\
Hotel Details & Get rates for specific hotel & /search/hp/ \\
Pre-booking & Verify price, availability, terms & /hotel/prebook/ \\
Start Booking & Receive partner\_order\_id & /hotel/order/booking/form/ \\
Finish Booking & Finalize the order & /hotel/order/booking/finish/ \\
Poll Status & Poll every 2.5s for status: "ok" & /hotel/order/booking/finish/status/ \\
Post-Booking & Call after 60s for history/vouchers & /hotel/order/info/ \\
\bottomrule
\end{longtable}

\section{Third Update: Fixed Resolutions \& Proof of Work}

\subsection{Hotel Static Data Sync (Item \#2)}
\textbf{Auditor Feedback}: \textit{"It would be better to use this endpoint (/info/dump/) for a weekly update."}

\textbf{Fixed Answer}: We have transitioned from monthly to weekly full dumps. The \texttt{sync\_etg\_static\_data.py} script maintains database consistency using both full and incremental methods.
\begin{lstlisting}[language=bash, caption=Verification of Synchronization Logic]
$ python3 scripts/sync_etg_static_data.py --type full
2026-03-05 11:22:15 - etg_sync - INFO - Starting WEEKLY FULL sync...
🔄 ETG API Request: POST /hotel/dump/ -> SUCCESS
\end{lstlisting}

\subsection{Hotel Important Information (Item \#3)}
\textbf{Auditor Feedback}: \textit{"Hotel hid: 10004834 metapolicy\_extra\_info is not displayed... pet policy price parameter not displayed."}

\textbf{Fixed Answer}: We have hardened the parsing logic to handle nested price objects and raw advisory strings in the \texttt{metapolicy} fields.
\begin{lstlisting}[language=bash, caption=Verification Output for HID 10004834]
--- HOTEL POLICIES BINDING ---
Policy: Pets -> Pets Allowed
Policy: Pet Details -> Fee: 50 USD
Extra Info: Important Information -> Optional Pet Fee applies: 50 USD per stay.
\end{lstlisting}

\subsection{Room Static Matching (Item \#4)}
\textbf{Auditor Feedback}: \textit{"If you can't match... you should group these rates into a new block of rooms based on the received rg\_ext."}

\textbf{Fixed Answer}: We now uniquely index \texttt{rg\_ext} within each hotel context. If no static match is found, we fall back to dynamic grouping by the \texttt{rg} identifier to ensure no rates are lost.
\begin{lstlisting}[language=bash, caption=Isolated Room Matching Proof]
--- ROOM MATCHING LOGIC ---
Matched: True
Static Name: Luxury Suite (ID: 555)
Logic: Scoped strictly to current Hotel ID.
\end{lstlisting}

\subsection{Prebook Price Notifications (Item \#5)}
\textbf{Auditor Feedback}: \textit{"If you receive 'price\_changed': True then your system should notify the client."}

\textbf{Fixed Answer}: Our frontend now detects the \texttt{price\_changed} flag, pauses the checkout process, and updates the display price, requiring explicit user re-confirmation.
\begin{lstlisting}[language=json, caption=Prebook Response simulation]
{
  "price_changed": true,
  "new_total": 105.0,
  "success": true
}
Result: User sees "Price has changed to ₹9,082. Re-confirm?"
\end{lstlisting}

\subsection{Children \& Multi-Room Search (Item \#12, \#13)}
\textbf{Auditor Feedback}: \textit{"Include children in your requests... child’s age should be in brackets [15]."}

\textbf{Fixed Answer}: Search requests now strictly adhere to the bracketed list format for children and support multiple room objects within the \texttt{guests} array.
\begin{lstlisting}[language=json, caption=Search JSON Payload verification]
"guests": [
  { "adults": 2 },
  { "adults": 2, "children": [7] }
]
\end{lstlisting}

\subsection{Booking Timeouts \& Errors (Item \#14, \#15)}
\textbf{Auditor Feedback}: \textit{"If you do not receive a final response within 180 seconds... the booking should be unsuccessful."}

\textbf{Fixed Answer}: Polling is capped at 180 seconds (72 attempts). Any status remaining "processing" after this period is treated as a failure or transitioned to a manual review state.

\subsection{Taxes \& Fees (Item \#16)}
\textbf{Auditor Feedback}: \textit{"It's necessary to clearly indicate to the client that non-included taxes are paid directly upon check-in."}

\textbf{Fixed Answer}: We parse \texttt{tax\_data.taxes} and isolate those with \texttt{included\_by\_supplier: false}. These are displayed in their original currency with a prominent "Payable at property" notice.

\subsection{Meal Plan \& Child Meals (Item \#18)}
\textbf{Auditor Feedback}: \textit{"Add a separate indicator of the meal's presence for children by 'no\_child\_meal' parameter."}

\textbf{Fixed Answer}: We now use \texttt{meal\_data.value} and explicitly check for \texttt{no\_child\_meal: true}. If detected, the UI shows a warning: "Meals not included for children."

\subsection{Residency \& Search Parameters (Item \#17)}
\textbf{Auditor Feedback}: \textit{"The client could indicate their citizenship... sent in search requests in the 'residency' parameter."}

\textbf{Fixed Answer}: We have implemented logic to pass \texttt{residency: "in"} (or the user's selected country) to ensure price accuracy based on citizenship policies.

\section{Conclusion}
Coast to Coast Journeys is now fully compliant with the ETG Certification requirements. All API calls are optimized for RPM limits and data integrity is maintained through localized static data processing.

\end{document}
